Introduction to Marginal Structural Models

### 2017-08-03 msm_introduction.Rmd
updated.

@@

@@

>>>>

- In the example, we want to know the average effect of a binary treatment for HIV (A) on continous CD4 counts (Y). Treatment is administered at multiple time points, with the only other covariate being a binary cutoff of HIV viral load (Z), where Z = 1 for viral load > 200 copies/ml. Further, viral load influences the decision to treat at that time point.

@@

## Testable research questions

- There are a couple that come to mind:

1. What is the average level of CD4 counts in those that received treatment at time 0 compared to those never treated?

@@

We'd like to know the average effect of treatment (at both time points)
